%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer, Data Platform team} % Job title
    {TikTok} % Organization
    {Mountain View, CA} % Location
    {Jun. 2020 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained TikTok's logging and data ingestion system (Flink, Kafka, Go, Python)}
        \item {Added features to the A/B testing platform (Python)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, Growth and Traffic team} % Job title
    {AirBnB} % Organization
    {San Francisco, CA} % Location
    {Dec. 2018 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built offline and real time components for customer data platform (Flink, Kafka, Spark, Scala, Hive, Airflow)}
        \item {Rewrote the visitor-user mapping pipeline, that infers a visitor's user id across different platforms (Spark, Scala)}
        \item {Maintained and improved data pipelines that prepare marketing summary and visits data. (Ruby on Rails, MySQL, Hive, Airflow)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Machine Learning Engineer, Big Data Machine Learning team} % Job title
    {Yahoo!} % Organization
    {Sunnyvale, CA} % Location
    {Feb. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Stabilized Spark based method to launch parameter server instances (Spark, Scala)}
        \item {Used TensorFlowOnSpark to generate word embeddings (word2vec), and optimize performance (Python)}
        %\item {Made enhancements to parameter server based LDA (Scala)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, Gemini ads team} % Job title
    {} % Organization
    {} % Location
    {Nov. 2016 - Feb. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built offline model training and feature engineering pipelines for ads ranking (Pig, Oozie, HDFS, Python, Java, Shell, Hive)}
        \item {Added features for online ads scoring service (C++)}
        \item {Developed an internal reporting tool for ads data visualization based on the open source web application,
Superset (Python, SQL, JavaScript)}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Applications Developer} % Job title
    {Third Wave Systems} % Organization
    {Minneapolis, MN} % Location
    {Jul. 2015 - Nov. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and implemented a new GUI de novo for a machining process simulating software}
        \item {Used C++ Open Cascade library for 3D geometry rendering and integrated it into GUI (java) using Java Native Interface (JNI)}
        \item {Added a semi-automated report generation feature (Java and C++)}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
